tl20-05_berghei_pir_DESEQ

### 2021-04-29 Manuscript_pirAnalysis_Github/Pberghei/Manuscript_berghei_pir_DESEQ.Rmd
Saving supp info for deseq stats berghei

```{r load_packages}
library('dplyr')
library('readr')
library('readxl')
library('data.table')
library('tibble')
library('ggplot2')
library('stringr')
library('RColorBrewer')
library('DESeq2')
```

@@

```{r gamMale_v_asexMix}
coef <- "stage_Gam.Male_vs_Asex.Mixed"
dds.deseq.gamMale_v_asexMixed.lfcShr <- lfcShrink(dds.deseq, 
                                                  coef = coef,
                                                  type = "apeglm")
gamMale_v_asexMixed_df <- as.data.frame(
  dds.deseq.gamMale_v_asexMixed.lfcShr[rownames(dds.deseq.gamMale_v_asexMixed.lfcShr) %in% c('PBANKA_0317181'),]
) %>% 
  mutate(contrast = coef)
```

@@

livMeroz_v_asexMixed_df <- as.data.frame(
  dds.deseq.livMeroz_v_asexMixed.lfcShr[rownames(dds.deseq.gamMale_v_asexMixed.lfcShr) %in% c('PBANKA_0100500',
                                                                                              'PBANKA_0600031'),]) %>%  
  mutate(contrast = coef)
```

@@

dds.deseq.asexRing_v_asexMixed.lfcShr <- lfcShrink(dds.deseq, 
                                                  coef = coef,
                                                  type = "apeglm")
asexRing_v_asexMixed_df <- as.data.frame(
  dds.deseq.asexRing_v_asexMixed.lfcShr[rownames(dds.deseq.asexRing_v_asexMixed.lfcShr) %in% c('PBANKA_1300200'),]
) %>% 
  mutate(contrast = coef)
```

@@

(livMeroz_v_gamMale_df <- as.data.frame(
  dds.maleGam.deseq.livMeroz_v_gamMale.lfcShr[rownames(dds.maleGam.deseq.livMeroz_v_gamMale.lfcShr) %in% c('PBANKA_0317181',
                                                                                                           'PBANKA_0100500',
                                                                                                           'PBANKA_0600031'),]
  ) %>%  
  mutate(contrast = coef))
```

```{r}
bind_rows(livMeroz_v_gamMale_df, 
          as.data.frame(gamMale_v_asexMixed_df),
          as.data.frame(livMeroz_v_asexMixed_df)) %>% 
  mutate(FDR = p.adjust(pvalue, 
                        method = 'fdr')) %>% 
  select(-c(lfcSE, 
            padj, 
            pvalue))
```

>>>>

```{r load_packages}
library('dplyr')
library('readr')
library('readxl')
library('writexl')
library('data.table')
library('tibble')
library('ggplot2')
library('stringr')
library('RColorBrewer')
library('DESeq2')
```

@@

```{r gamMale_v_asexMix}
coef <- "stage_Gam.Male_vs_Asex.Mixed"
dds.deseq.gamMale_v_asexMixed.lfcShr <- lfcShrink(dds.deseq, 
                                                  coef = coef,
                                                  type = "apeglm")
gamMale_v_asexMixed_df <- as.data.frame(
  dds.deseq.gamMale_v_asexMixed.lfcShr[rownames(dds.deseq.gamMale_v_asexMixed.lfcShr) %in% c('PBANKA_0317181'),]
) %>% 
  mutate(contrast = coef) %>% 
  rownames_to_column(var = 'Geneid')
```

@@

livMeroz_v_asexMixed_df <- as.data.frame(
  dds.deseq.livMeroz_v_asexMixed.lfcShr[rownames(dds.deseq.gamMale_v_asexMixed.lfcShr) %in% c('PBANKA_0100500',
                                                                                              'PBANKA_0600031'),]) %>%  
  mutate(contrast = coef) %>% 
  rownames_to_column(var = 'Geneid')
```

@@

dds.deseq.asexRing_v_asexMixed.lfcShr <- lfcShrink(dds.deseq, 
                                                  coef = coef,
                                                  type = "apeglm")
asexRing_v_asexMixed_df <- as.data.frame(
  dds.deseq.asexRing_v_asexMixed.lfcShr[rownames(dds.deseq.asexRing_v_asexMixed.lfcShr) %in% c('PBANKA_1300200'),]
) %>% 
  mutate(contrast = coef) %>% 
    rownames_to_column(var = 'Geneid')
```

@@

(livMeroz_v_gamMale_df <- as.data.frame(
  dds.maleGam.deseq.livMeroz_v_gamMale.lfcShr[rownames(dds.maleGam.deseq.livMeroz_v_gamMale.lfcShr) %in% c('PBANKA_0317181',
                                                                                                           'PBANKA_0100500',
                                                                                                           'PBANKA_0600031'),]
  ) %>%  
  mutate(contrast = coef) %>% 
    rownames_to_column(var = 'Geneid'))
```

```{r}
(deseq_stats <- bind_rows(livMeroz_v_gamMale_df, 
          as.data.frame(gamMale_v_asexMixed_df),
          as.data.frame(livMeroz_v_asexMixed_df)) %>% 
  mutate(FDR = p.adjust(pvalue, 
                        method = 'fdr')) %>% 
  select(-c(lfcSE, 
            padj, 
            pvalue)))
```

```{r save_stats_df}
write_xlsx(deseq_stats, 
           'SupplementaryInformation_Stats_DESEQ_berghei.xlsx')
```
